\documentclass{article}

\begin{document}

\begin{center}
    \huge{\textbf{WhiteBoard}}
    
    \huge{\textit{An Efficient and Intuitive Learning Management System}}

    \huge{Project Proposal}

    \vspace{10 pt}

    \large{
        \begin{tabular}{cccc}
            Joel Kottas&Noah Christiano&Jacob Roschen&Shir Maimon\\
        \end{tabular}
    }

\end{center}

\vspace{10 pt}

\section{Background}

A Learning Management System(LMS) is an interface between students, professors,
and school administration. One of the most popular LMSes, especially at
colleges and universities, is Blackboard. Blackboard, however, like other
LMSes, is extremely slow and has unnecessary features that are often left
unused. For example, Blackboard’s personalize page features are rarely used,
and students avoid the discussion boards. These LMSes’ designs also often make
them difficult to navigate. For example, Blackboard has two sets of navigation
tabs, and it is not obvious what the difference between them is. These problems
add up to create an interface that is slow and difficult to use, even though
there is no need for it to be that way. Students today would rather get what
they need quickly than have hundreds of features that they rarely, if ever,
use. Other LMSes exist too, such as Moodle, Veracross, and Canvas, but they
have their own problems, and none of them are open-source or as lightweight as
we want.

\section{Objective}

WhiteBoard will focus on having an efficient, intuitive interface, and it will
have features of excellent quality rather than a large quantity of features. It
is open-source, allowing it to be customized and used as desired, it focuses on
the University of Rochester. Most importantly, WhiteBoard will have a unified
user experience. It shouldn’t take a student who is majoring in computer
science three days to find where the grades are posted, and even then to be
confused about what their grade is, and it should be easy to navigate to the
University of Rochester website. WhiteBoard’s design will make such navigation
a pleasure.

\section{Features}

Specifically, WhiteBoard will have the following features:
\begin{itemize}
    \item Lightning-quick load times
    \item A secure and painless login system
    \item Course system, with registration and grades for students
        \begin{itemize}
            \item Possibly a bonus schedule optimizing utility
        \end{itemize}
    \item Calendar
    \item Convenient communication between administrators, professors, and
        students, both for general communication and announcements
    \item Open source
\end{itemize}

\section{Current Assets}

Our team’s combined experience covers PHP and Javascript very well, the
LAMP stack and all its associated programming languages, and even
configuring a Linux server for web hosting. Everyone on the team
understands design, and how to learn from both the successes and the
mistakes of systems like Blackboard. As students, we have constant access
to Blackboard, and we have the expertise to dive into the site to see what
code works well and what code doesn’t. We are also constantly learning, and
our ability in areas relating to this project will only increase.

We are also using several libraries to assist in creating WhiteBoard. We
are using jQuery, a javascript library, and code from the open source
PHP-Login project, so that we have a secure but simple to use system.

\section{Budget}
A large budget shouldn’t be necessary. WhiteBoard requires server space on
which it can be hosted, but we are planning to get server space on the computer
science servers to save money. If we can’t get server space there, then we
shouldn’t need to spend more than \$10 per month on hosting.

\section{Schedule}

\begin{tabular}{ll}
    Weeks 1-2&Project proposal and brainstorming\\
    Weeks 3-4&Set up development environment and plan database structure\\
    Weeks 5-6&Implement login system and general layout\\
    Weeks 7-8&Implement courses and grades\\
    Weeks 9-10&Implement annoucements and communication\\
    Weeks 11-12&Implement schedule/calendar, maybe with schedule optimizer\\
    Week 13&Prepare for presentation\\
\end{tabular}

\section{Responsibilities}

%\begin{tabular}{ll}
%    Joel&GitHub/git management, presentation design, LaTex programming\\
%    Noah&Database structure, server management, efficiency analyst\\
%    Jacob&Project lead, database structure\\
%    Shir&Site design, documentation, scaling/hardware compatibility\\
%    All&Site development\\
%\end{tabular}

\nocite{*}

\bibliography{refs}{}
\bibliographystyle{acm}

\end{document}
