\documentclass[12 pt]{article}

\usepackage[margin=1 in]{geometry}

\begin{document}

\begin{center}

    \huge{\textbf{WhiteBoard}}

    \huge{\textit{Joel's Individual Report}}

\end{center}

\vspace{10 pt}

\section{Qualitative}

\subsection{Proposals and Reports}

I am the primary author of the proposals and the reports. I wrote all the LaTeX
code (of course, I didn't write all the prose; I wrote some and copied in what
my teammates wrote), and most of the prose in each of the documents. I estimate
this to be around 1-2 pages total, although I'm horrible at estimating, so that
could be way off.

\subsection{Organization}

I've been the primary organizer of the code, and I'm the best at Git in the
team, so I do much of the merging of code.

\subsection{Database}

I was one of the primary database designers. We only had minimal database
changes after the initial designing, so we did a quality job designing it
initially.

\subsection{Front-end Coding}

I wasn't as active in this area, but I did do some minor fixes here.

\section{Quantitative}

\subsection{Hours}

On average, I think I spend 2 hours per week on this project, but this varies
very much week to week.

\subsection{Commits}

Not including merge commits, I have done 69 commits so far that have gone into
the master branch.

\subsection{Lines of Code}

I have written approximately 7792 and removed approximately 7804 lines of code.
This is mostly based what Github has recorded, with some manual adjustment as
necessary.

\end{document}
