

Project Progress Report

12 Minute (+ 3 mins for questions) public presentation or written document or
(better) both, date TBA, sometime uncomfortably close.

One grade per team.  So each team member should be involved
with the production and final approval of the form and content of the
presentation.  Useful preparation --  look over:  Orig. Proposal and 
CB's critique, Revised Proposal and CB's critique of that.  Team
Liaisons should (and should have) provide team with these materials.

Report can be a (PPT style) presentation, or written document, or both.
    BB Hand In: Convert all materials to .pdf and hand in by due date on BB.
    Presentation Pre-Handover: Get CB a copy of any electronic presentation
    materials (e.g. a .ppt file) by 0900 the morning of the show and he'll load
    them on his computer

    Short talks are very hard. Rehearse, perferably in front of an audience
    (other teams would be good). Get criticism, get time down to 12 minutes.
    Rehearse!



----------sample format---------



Quick Review

   Goals
   Scholarship (Prior work, references)
   Technical approach.  Components and how they fit together.  Should
   match the Individual Report categories.


Individual Reports
 These are mandatory. Do whatever it takes to work them into report.

  Each team member contributes  ``by-lined'' section(s) of presentation
  or document.  (One presenter for whole show is fine, however).


Current Collective State
   Summary
   Demonstration if possible
   Credible Timeline and Milestones (significant partial goals, what
   and when).







